Towards Verifying the Bitcoin-S Library

### 2019-06-21 paper/paper.tex
add before and after for & function

Due to the restrictions on BigInt, we can not use the \& function either.
Simplified code:
\begin{lstlisting}[style=scala]
  sealed abstract class Number extends BasicArithmetic[Int64] {
    def andMask: BigInt

    override def +(num: Int64): Int64 = apply(checkResult(underlying + num.underlying))

    private def checkResult(result: BigInt): BigInt = {
      require((result & andMask) == result, "Result was out of bounds, got: " + result)
      result
    }
  }
\end{lstlisting}

>>>>

Due to the restrictions on BigInt, we can not use the \& function either.
Before:
\begin{lstlisting}[style=scala]
sealed abstract class Number {
  type A = BigInt

  /**
    * Checks if the given result is within the range
    * of this number type
    */
  private def checkResult(result: BigInt): A = {
    require(
          result <= BigInt("9223372036854775807")
      && result >= BigInt("-9223372036854775808"),
      "Result was out of bounds, got: " + result)
    result
  }
}

/**
  * Represents a int64_t in C
  */
sealed abstract class Int64 extends SignedNumber {
  override def apply: A => Int64 = Int64(_)
}
\end{lstlisting}
